---
title: "Week 3"
author: "Noah Jones"
date: "3/6/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

# Resources

Today we are going to try to figure out how to fit to a distribution. [This](https://www.cyclismo.org/tutorial/R/linearLeastSquares.html) might be a useful resource.

```{r Looking at the Normal Distribution}
hist(rnorm(1000), breaks = 20)
plot(dnorm(seq(-1, 1, 0.01)), type = 'l')
plot(pnorm(seq(-1, 1, 0.01)), type = 'l')
```

It looks like the probability density function is what we are probably looking for. To generate a linear model, we have to describe the two data sets such that they vary together. Perhaps the quantiles co-vary, or their ranks co-vary. Something like that. I think quantiles might be the most appropriate.

```{r}
plot(qnorm(seq(.001, .999, .001)), type = "l")
```

```{r}
v <- quantile(rnorm(1000), seq(.01, .99, .01)) - 
  qnorm(seq(.01, .99, .01))
plot(v)
```

# Quantile Plots

We demonstrate that by plotting the quantiles of a dataset against the quantiles of a distribution, we can infer whether the data set matches the distribution.

```{r Q-Q Plot for Normal Distribution}
cbind(quantile(rnorm(1000)*10, seq(.01, .99, .01)), qnorm(seq(.01, .99, .01))) %>% 
  data.frame() -> df1
plot(X1 ~ X2, df1)
lm(X1 ~ X2, df1) %>% summary()
```



```{r Normal Distribution}
cbind(quantile(runif(1000)*10, seq(.01, .99, .01)), qnorm(seq(.01, .99, .01))) %>% 
  data.frame() -> df2
plot(X1 ~ X2, df2)
lm(X1 ~ X2, df2) %>% summary()
```

```{r Uniform Distribution}
cbind(quantile(runif(1000)*10, seq(.01, .99, .01)),
      qunif(seq(.01, .99, .01))
      ) %>% 
  data.frame() -> df3
plot(X1 ~ X2, df3)
lm(X1 ~ X2, df3) %>% summary()
```

```{r Poison Distribution}
cbind(quantile(rpois(1000, 10)*10, seq(.01, .99, .01)), 
      qpois(seq(.01, .99, .01), 10)
      ) %>% 
  data.frame() -> df3
plot(X1 ~ X2, df3)
lm(X1 ~ X2, df3) %>% summary()
```
```{r Other Distributions}
rnorm(100) %>% hist(breaks = 10, main = "Normal")
runif(100) %>% hist(breaks = 10, main = "Uniform")
rbinom(100, 1, 0.5) %>% hist(breaks = 2, main = "Binomial")
rpois(100, 10) %>% hist(breaks = 10, main = "Poison")
rhyper(100, 1000, 500, 200) %>% 
  hist(breaks = 10, main = "Hyper")
sample(1:6, 100, replace = T, prob = rep(1/6,6)) %>% 
  hist(breaks = 10, main = "Sampling with Replacement")
rcauchy(100) %>% hist(breaks = 10, main = "Cauchy")
rchisq(100, 4) %>% hist(breaks = 10, main = "Chi Squared")
rgamma(100, 1, 0.5) %>% hist(breaks = 10, main = "Gamma")
rlnorm(100, 0, 1) %>% hist(breaks = 10, main = "Log Normal")
rt(100, 10) %>% hist(breaks = 10, main = "Student's")
```

